week getbackontrack

### 2024-11-23 estimate_M3.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Estimate_M2"
author: "Verooo"
date: "2024-11-22"
output: html_document
---

@@

MODEL 2
Testing if the models can be estimated in separate files without error. Easier for me than cleanign the workspace due to oversight of having separate tabs. Of course I still clean the workspace in between but yaknow. Visual distinction.

# Setup
clean workspace
```{r clean}
rm(list = ls())
```

@@

## Model 2 - Gender

**CHANGE** Model 2 builds on Model 1 and includes the network statistics
for gender: diffX, diffXTransTrip, egoX & altX. This model has a
convergence of 0.23 and a Goodness of Fit on the indegree distribution
of 0.184. For the structural network statistics we find similar results,
in terms of estimate size and significance, as in Model 1. However, the
outdegree activity parameter almost reaches significance (-1.7135484).
With regard to the covariate network statistics, we find that the gender
of ego (egoX), the gender of alter (altX) and the difference between ego
and alter (diffX) is not significant and thus the estimate cannot be
trusted. The transtrip for different gender (diffXTransTrip) is positive
and significant, which implies that an ego prefers to close triads with
alters who have a different gender score than theirs. This is an
interesting finding, because it implies that their is a tendency towards
diverse collaboration. However, when compared to the level of gender
clustering and the fact that this clustering decreased, this finding
does make sense.

@@

```{r RSiena define m2}
# dependent variable 
nets <- sienaDependent(net_array)

@@

# define data object 
mydata_M2 <- sienaDataCreate(nets, gender_RS)

@@

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

#if there is not a folder called "results" in your repository: make one

@@

```{r}
print01Report(mydata_M2, modelname = "./results/results_M2") # create file with report in results folder 
```

@@

```{r RSiena myeff m2}
# define effects structure 
myeff_M2 <- getEffects(mydata_M2)

@@

```{r effects m2}
myeff_M2 <- includeEffects(myeff_M2, isolateNet, inPop, outAct)

myeff_M2 <- includeEffects(myeff_M2, egoX, altX, sameX, interaction1 = "gender_RS")

### Step 4: Specify model/algorithm

```{r algo m2}

myAlgorithm_M2 <- sienaAlgorithmCreate (projname = "results_M2")

@@

```{r estimate m2}
# estimate the model 
Model2 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, returnDeps = TRUE)
#latter needed for GOF

Model2

@@

```{r GOF M2}
GOF_M2 <- sienaGOF(Model2, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M2, main = "GOF - Model 2 \n Indegree Distribution")
```

>>>>

---
title: "Estimate_M3"
author: "Verooo"
date: "2024-11-22"
output: html_document
---

@@

MODEL 3 - Gender & H-index 
Testing if the models can be estimated in separate files without error. Easier for me than cleanign the workspace due to oversight of having separate tabs. Of course I still clean the workspace in between but yaknow. Visual distinction.

# Setup
Clean workspace.
```{r clean}
rm(list = ls())
```

@@

## Model 3 - H-Index

**CHANGE!!!** Model 3 includes the covariate network statistics for
Prestige: egoX, altX and inPopX. This model has a convergence ratio of
0.23 and a a Goodness of Fit on the indegree distribution of 0.64. In
this model, the parameters for density and reciprocity are still
significant, with values of -1.98 (se = 0.71) and 2.59 (se = 0.38)
respectively, meaning that actors prefer sparse networks, but do prefer
to send ties to alters who have sent ties to them. IsolateNet is still
significant with a value of 3.23 (se = 1.06), implying that actors
prefer to be isolates. In this model, indegree popularity squared (b =
0.17, se = 0.21) is no longer significant, implying that this might be
explained by other network statistics in the model. The covariate
statistics for gender show similar findings as Model 2 & Model 2.5,
namely that actors prefer to close triads with alters that have a
different score for gender (b = 1.51, se = 0.44). the ego effect and
alter effect for gender are non-significant, as was the case in Model 2
& Model 2.5. Lastly, Model 3 shows some significant results with regards
to the covariate network statistics for prestige. The prestige effect
for alters is positive, implying that people prefer to send ties to
people who have a higher amount of prestige (b = 0.042, se = 0.0089).
Additionally, the prestige effect for egos is negative, which indicates
that people who have higher prestige send less ties (b = -0.030, se =
0.015). This is in line with theories of preferential attachment and
upward mobility, because as egos with higher prestige will are more
likely to receive request for collaboration rather then sending request
for collaboration. Interestingly enough, the indegree popularity
statistic for prestige is not significant (b = -0.012, se = 0.023),
implying that actors who are more prestigious do not receive more
indegrees.

@@

```{r RSiena define m3}
# dependent variable 
nets <- sienaDependent(net_array)

@@

# put h-index in object 
h_index <- df_ego$h_index
df_ego$h_index

# covariate 2
h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena

# define data object 
mydata_M3 <- sienaDataCreate(nets, gender_RS, h_index_RS)

@@

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)
# if there is not a folder called "results" in your repository: make one

@@

```{r}
print01Report(mydata_M3, modelname = "./results/results_M3") # create file with report in results folder 
```

@@

```{r RSiena myeff M3}

# define effects structure 
myeff_M3 <- getEffects(mydata_M3)

@@

```{r effects M3}
myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPop, outAct) # model1

myeff_M3 <- includeEffects(myeff_M3, egoX, altX, sameX, interaction1 = "gender_RS") # model2

myeff_M3 <- includeEffects(myeff_M3, egoX, altX, inPopX, interaction1 = "h_index_RS") # model3

```
<!-- # isolatenet: if individual is alone they "like to/tend to stay alone"
# inPop: ppl like to collab with people who are popular

# change statistics to fit whatever I want to know about h-index 
# not sameX 
# look up inPopX: preferential attachment (cf. Koen lel), higher h-index more popular 
  # cf. Fridas modeling process (Jochem told her that )
-->
### Step 4: Specify model/algorithm

```{r algo M3}

myAlgorithm_M3 <- sienaAlgorithmCreate (projname = "results_M3")

@@

```{r estimate M3}
# estimate the model 
Model3 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, returnDeps = TRUE)
#latter needed for GOF

Model3

@@

```{r GOF M3}
GOF_M3 <- sienaGOF(Model3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M3, main = "GOF - Model 3 \n Indegree Distribution")
```

### 2024-11-23 revisitwithJochem.Rmd
modelestimates-GOFs-desresults-darkgraph

myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this
```

>>>>

myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this
# NOW ITS DIRECTED SO USE DIFFERENT MODELTYPE FOR ALGORITHM 
```

### 2024-11-23 week5-2.Rmd
modelestimates-GOFs-desresults-darkgraph

# 7.13 STEP 4: Specify model 
Sometimes similartostep 2 (but here you include specifically the effects you want to look at)
```{r}
# if you want to select only specific effects in your model:

@@

```
over time:
inpope ppl with lots of indegrees will havelot of indegrees later (in population)
 outAct ppl with lots of outdegrees will have lot of indegrees later

@@

# Sidenote: H- index via openAlex

@@

# STUDY CHAPTER 12 of RSiena Manual! 
# PrACTICE WITH RSIENA

# DONT GO OVERBOARD!!! 
# REMAIN FOCUSED!!!

>>>>

# 7.13 STEP 4: Specify model 
Sometimes similartostep  (but here you include specifically the effects you want to look at)2
```{r}
# if you want to select only specific effects in your model:

@@

```
over time:
inpop: ppl with lots of indegrees will havelot of indegrees later (in population)
 outAct: ppl with lots of outdegrees will have lot of indegrees later

@@

## Sidenote: H- index via openAlex

@@

# STUDY CHAPTER 12 of RSiena Manual! 
## PrACTICE WITH RSIENA 
# DONT GO OVERBOARD!!! & REMAIN FOCUSED!!!

### 2024-11-23 weekbacktrack.Rmd
modelestimates-GOFs-desresults-darkgraph

| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods           | ![](images/socialnetworking_meh.jpg)*[university]*write introduction, and theory [W] |

@@

| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       |                                                                            |                                                                                      |

>>>>

| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods outline   | ![](images/socialnetworking_meh.jpg)*[university]*write introduction, and theory [W] |

@@

| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | write Data part [W]                                                           | Make darkmode bc my eyes will fall out                                     |                                                                                      |
